Artin Group Presentations Arising from Cluster Algebras

### 2014-09-08 Paper.tex
More Edits

@@

\begin{lem} \label{Sym-Lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:

\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

The structure of the proof will be analogous to the structure of the proof of Theorem \ref{thm:barot_and_marsh_A}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.  In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem \ref{thm:barot_and_marsh_A} rely heavily on the $(R1)$ relations and therefore did not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.

Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively. Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.  In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.

@@

\item This follows from part (i) by symmetry
\end{enumerate}
\end{enumerate}
\end{proof}

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We would also like to thank the University of Minnesota School of Mathematics for hosting us. We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem. We thank Emily Gunawan for her useful comments on our work. We also thank Vic Reiner for helping Gregg Musiker pose the problem.}

>>>>

   \item[(h)]
   \begin{tikzpicture}[baseline=-0.5ex]

@@

\begin{lem} \label{Sym-Lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

The structure of the proof will be analogous to the structure of the proof of Theorem A in \cite{BM13}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.  In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem A rely heavily on the $(R1)$ relations and therefore do not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.

Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively. Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.  In order to distinguish the relations in the groups $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we shall refer to the relations on $A_{\Gamma}$ as $(T2),(T3)$ and the relations on $A_{\Gamma^\prime}$ as $(T2^\prime),(T3^\prime).$ In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.

@@

\item This follows from part (i) by symmetry.
\end{enumerate}
\end{enumerate}
\end{proof}

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We would also like to thank the University of Minnesota School of Mathematics for hosting us. We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem. We thank Emily Gunawan for her useful comments on our work. We also thank Vic Reiner for motivating this problem.}
